### 2017-10-13 Gruba/03-fe.tex

TF-IDF based similarity is then calculated.
For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t),
\end{equation}
where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.

>>>>

TF-IDF based similarity is then calculated.
%For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined %as:
%\begin{equation}
%\label{eq:sim-tf1}
%sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t),
%\end{equation}
%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
For example, the similarity of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as formula \ref{eq:sim-tf1}.
Here $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, $VEC_{W_f}$ is defined as formula \ref{eq:sum-tf1}, $VEC_t$ is defined as formula \ref{eq:sum-lexion},
where $N_t$ is the number of words in topic $t$ and $vec[w]$ is the word vector of word $w$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = VEC_{W_f} \cdot VEC_t
\end{equation}
\begin{equation}
\label{eq:sum-tf1}
VEC_{W_f} = \sum_{\substack{i}} p_i*vec[w_i]
\end{equation}
\begin{equation}
\label{eq:sum-lexion}
VEC_t = \sum_{\substack{j}} \frac{1}{N_t}*vec[c_j]
\end{equation}
%where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector %\cite{IEEEexample:mikolov2013distributed}.
